High-Fidelity Counterfactual Explanations through Conformal Prediction

### 2023-05-19 notebooks/mnist.qmd
polishing repo

    for (_name,ce) in collect(ces)[_plt_order]
        _x = CounterfactualExplanations.counterfactual(ce)
        _phat = target_probs(ce)
        _title = "($(letters[_count]))"
        plt = Plots.plot(
            convert2image(MNIST, reshape(_x,28,28)),
            axis=([], false), 
            size=(img_height, img_height),
            title=_title
        )
        plts = [plts..., plt]
        _count += 1
    end
    # plts = plts[_plt_order]
    # plts = [p1, plts...]
    plt = Plots.plot(plts...; size=(img_height,img_height))

@@

```{julia}
_regen_all_digits = true
if _regen_all_digits
    function plot_all_digits(rng=123;verbose=true,img_height=180,kwargs...)
        plts = []
        for i in 0:9
            for j in 0:9
                @info "Generating counterfactual for $(i) -> $(j)"
                plt = plot_mnist(i,j;kwargs...,rng=rng, img_height=img_height)
                !verbose || display(plt)
                plts = [plts..., plt]
            end
        end
        plt = Plots.plot(plts...; size=(img_height*10,img_height*10), layout=(10,10), dpi=300)
        return plt
    end
    plt = plot_all_digits(generator=eccco_generator)
    savefig(plt, joinpath(output_images_path, "mnist_eccco_all_digits.png"))
end
```

>>>>

    for (_name,ce) in collect(ces)[_plt_order]
        _x = CounterfactualExplanations.counterfactual(ce)
        _phat = target_probs(ce)
        _title = "($(letters[_count]))"
        plt = Plots.plot(
            convert2image(MNIST, reshape(_x,28,28)),
            axis=([], false), 
            size=(img_height, img_height),
            title=_title
        )
        plts = [plts..., plt]
        _count += 1
    end
    plt = Plots.plot(plts...; size=(img_height,img_height))

@@

```{julia}
_regen_all_digits = false
if _regen_all_digits
    function plot_all_digits(rng=123;verbose=true,img_height=180,kwargs...)
        plts = []
        for i in 0:9
            for j in 0:9
                @info "Generating counterfactual for $(i) -> $(j)"
                plt = plot_mnist(i,j;kwargs...,rng=rng, img_height=img_height)
                !verbose || display(plt)
                plts = [plts..., plt]
            end
        end
        plt = Plots.plot(plts...; size=(img_height*10,img_height*10), layout=(10,10), dpi=300)
        return plt
    end
    plt = plot_all_digits(generator=eccco_generator)
    savefig(plt, joinpath(output_images_path, "mnist_eccco_all_digits.png"))
end
```
